### 2013-10-18 chi2014/method.tex

Initially, workers were randomly paired with a question from a pool of questions. However, we eventually dropped all other questions, so workers would only receive the MP3 player question. %When testing multiple questions, we attempted to prevent workers from answering the same question twice (for example, if they chose the HIT requesting 10 responses, then the HIT requesting 20 responses) . However, we were not always successful in preventing this from happening. Thus, we only use a worker's first set of responses if they answered the question multiple times.

@@

Upon accepting a HIT, participants were asked to give consent for participating in the study, and informed that they could leave the study at any point without financial consequences. Under more realistic, real-world conditions, workers would be expected to complete all responses to receive compensation.

@@

In total, 154 workers submitted 170 HITs, for a total of 3292 responses. As we received data in the unlimited condition, it became obvious that this was a poor strategy to employ -- the number of responses received was less than 15 in all cases. Accordingly, we remove that data from our analysis.

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the possibility that their responses and idea generation processes evolved over time, making it difficult to compare the responses to their second HIT with responses from others who are performing the same HIT for the first time. Accordingly, we retain only the first HIT submitted by each worker.

@@

\subsection{Hierarchical Clustering}
One of the primary goals of this research is to model the rate at which novel ideas and categories of ideas arrive. A significant challenge to creating these models is efficiently identifying what ideas and categories of ideas are similar to one another, given the volume of data collected. To address this problem, we organized the data into sets of hierarchical clusters, where the clusters encode similarity relationships between ideas. Specifically, parent nodes are more generalized versions of child nodes. With this information encoded in the clusters, we are then able to calculate quantities such as the rate of novel ideas or novel idea categories, as a function of responses received.

@@

The primary author clustered the 3007 response instances into ideas and category trees. A researcher not involved in the project randomly sampled 40 category trees to assess whether ideas within the tree should be there, and whether parent-child relationships correctly encoded generalizations of concepts. 10\% of the instances were marked as more specific than their associated idea, while 0.7\% of the instances were judged to be misclassified with their associated cluster.

>>>>

@@

Upon accepting a HIT, participants were asked to give consent for participating in the study, and informed that they could leave the study at any point without financial consequences. Under real-world conditions, workers would be expected to complete all responses to receive compensation.

@@

154 workers submitted 170 HITs, for a total of 3292 responses. As we received data in the unlimited condition, it became obvious that this was a poor strategy to employ -- the number of responses received was less than 15 in all cases. Accordingly, we remove that data from our analysis.

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the possibility that their responses and idea generation processes evolved over time. Accordingly, we retain only the first HIT submitted by each worker.

@@

\subsection{Hierarchical Clustering}
One of the primary goals of this research is to model the rate at which novel ideas and categories of ideas arrive. A significant challenge to creating these models is efficiently identifying what ideas and categories of ideas are similar to one another. To address this problem, we organized the data into sets of hierarchical clusters, where parent nodes are more generalized versions of child nodes. With this relationship, we are then able to calculate quantities such as the rate of novel ideas or novel idea categories, as a function of responses received.

@@

The primary author clustered the 3007 response instances into ideas and category trees. A researcher not involved in the project randomly sampled 40 category trees to assess whether ideas within the tree should be there, and whether parent-child relationships correctly encoded generalizations of concepts. 10\% of the instances were marked as more specific than their associated idea, while 0.7\% of the instances were judged to be misclassified with their associated cluster tree.
